Mainstreaming Race Science

### 2023-06-09 paper/paper.Rmd
readme for paper

---
title: "Mainstreaming Race Science"
authors:
  - name: "Daniel J. Hicks"
    affiliation: 1
    corresponding_author: true
  - name: "Emilio Lobato"
    affiliation: 1
address:
  - code: 1
    address: "University of California, Merced"
corresponding_author: "To whom correspondence should be addressed; E-mail: dhicks4@ucmerced.edu."
abstract: |
  Enter the text of your abstract here.
acknowledgements: |
  Please include your acknowledgments here, set in a single paragraph.
bibliography: "references.bib"
output: 
  # https://github.com/rstudio/rticles/pull/486
  rticles::science_article:
      keep_tex: true
      move_figures: false
      draft: false
      number_sections: true
---

>>>>

---
title: "Mainstreaming Race Science"
authors:
  - name: "Daniel J. Hicks"
    affiliation: 1
    corresponding_author: true
  - name: "Emilio Lobato"
    affiliation: 1
address:
  - code: 1
    address: "University of California, Merced"
corresponding_author: "To whom correspondence should be addressed; E-mail: dhicks4@ucmerced.edu."
abstract: |
  Enter the text of your abstract here.
acknowledgements: |
  Please include your acknowledgments here, set in a single paragraph.
bibliography: "references.bib"
output: 
  # https://github.com/rstudio/rticles/pull/486
  # skeleton: <https://github.com/christopherkenny/rticles/tree/master/inst/rmarkdown/templates/science>
  rticles::science_article:
      keep_tex: true
      move_figures: false
      draft: false
      number_sections: false
---
